Turbo fast no compromise gravitational wave parameter estimation

### 2022-11-02 src/tex/ms.tex
update accelerator part

@@

@@

@@

>>>>

In this section we give a self-contained summary the gravitational-wave parameter estimation process.

@@

Modern accelerators such as GPUs and TPUs are designed to execute large scale
dense computation. They are often much more cost-efficient than using many CPUs
when it comes to solving problems that can be benefited from parallelization.
The downside of these accelerators compared to CPUs is they can only perform a
more restricted set of operation, and are often less performant when they are
dealing with problem that are serial. Parameter estimation with MCMC is a serial
problem, since each new sample generated from a chain depends on the last sample
in the chain. This means naively putting the problem on an accelerator is more
likely to harm the performance instead of improving it.

In this work, the use of accelerators provides two independent perks that
tremendously benefits the parameter estimation process. First, using
accelerators allow us to run many independent chains at the same time, which
benefits the training of the normalizing flow. Since we generate the data we use
to train the normalizing flow on-the-fly, the more independent data we can feed
to the training process, the higher chance the normalizing flow can learn a
reasonable representation of the global landscape of the target distribution. If
we only use a small amount of chains, we are limited to the correlated samples
from each chain, so we have to run more sequential steps to get the same amount
of independent data as compared to running more chains, where former option does
not benefit from parallelization but the latter does. In another word, being
able to use many independent chains help the normalizing flow learn the global
landscape faster in WALL time.

Another benefit i

@@

\kw{GW159014}
\kw{GW170817}

@@

% Precessing waveforms and higher mode.
